---
title: "Ophys Single Session Analysis"
author: "Brennan Lagasse, Advised by Dr. Ethan Meyers"
date: "2023-3-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(NeuroDecodeR)
library(ggplot2)
library(dplyr)
library(tidyr)
library(foreach)

```



```{r load_raster_data}

raster_dir_name = file.path("R_OphysData", "session_496908818", "natural_scenes")
file_name = "517404519.rda"

load(file.path(raster_dir_name, file_name))

test_valid_raster_format(file.path(raster_dir_name, file_name))

plot(raster_data, main = "Test")

```


```{r bin_data}


save_dir_name <- file.path("R_OphysData_Binned", "session_496908818", "natural_scenes")

# Sampling interval is the amount of time between measures

binned_file_name <- create_binned_data(raster_dir_name,
                                       file.path(save_dir_name, "ZD"),
                                       2, 1)

# Technically -300 to -261

```

``` {r stimulus_counts}

label_rep_info <- get_num_label_repetitions(binned_file_name, "natural_scene_stimulus_id") 
plot(label_rep_info)  

```


**Decoding Analysis**

Performing a decoding analysis involves several steps:

1. Creating a datasource (DS) object that generates training and test splits of the data.

``` {r decode_datasource}

# Fewer groups for speed. Up to 50 seems appropriate
variable_to_decode <- "natural_scene_stimulus_id"
num_cv_splits <- 20
  
ds <- ds_basic(binned_file_name, variable_to_decode, num_cv_splits)


```

2. Optionally creating feature-preprocessor (FP) objects that learn parameters from the training data, and preprocess the training and test data.

``` {r decode_feature_processing}

fps <- list(fp_zscore())

```

3. Creating a classifier (CL) object that learns the relationship between the training data and training labels, and then evaluates the strength of this relationship on the test data.

``` {r decode_classifier}

cl <- cl_max_correlation()

```

4. Creating result metric (RM) objects that aggregate the predictions to create result summaries.

``` {r decode_results}

rms <- list(rm_main_results(), rm_confusion_matrix())

```

5. Running a cross-validator object that using the datasource (DS), the feature-preprocessor (FP) and the classifier (CL) objects to do a cross-validation procedure that estimates the decoding accuracy.

``` {r decode_cross_validate}

# Default parameters for a quick run (resamples increased to 50)

cv <- cv_standard(datasource = ds, 
                  classifier = cl, 
                  feature_preprocessors = fps, 
                  result_metrics = rms, 
                  num_resample_runs = 2)


```

``` {r run_analysis}

DECODING_RESULTS <- run_decoding(cv)

```

``` {r visualize_results} 

plot(DECODING_RESULTS$rm_main_results)

plot(DECODING_RESULTS$rm_main_results, results_to_show = 'all', type = 'line')

plot(DECODING_RESULTS$rm_confusion_matrix)

plot(DECODING_RESULTS$rm_confusion_matrix, results_to_show = "mutual_information")

```

